---
title: "Step Data Taken from Fitness Band"
output: html_document
---

#Load Data

```{r}
library(ggplot2)
setwd("C:/Users/jamshz/Documents/R/activity")
activity <-read.csv("activity.csv")
```

#Number of steps taken

```{r}
total<-aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
head(total)
```

#Histogram of steps taken

```{r}
hist(total$steps, breaks = seq(0,25000,1000))
```

#Averages of Steps Taken

```{r}
med.total <- median(total$steps)
mean.total <- mean(total$steps)
```

The mean number of steps taken is `r mean.total` and the medial number of steps taken is `r med.total`.

#Steps by Interval

```{r}
TSP <- aggregate(steps ~ interval, data = activity, mean, na.rm=TRUE)
with(TSP, plot(interval, steps, type="l"))
```

#Max steps taken in Interval

```{r}
maxSteps <- max(TSP$steps)
maxTSPRow <- which(grepl(maxSteps, TSP$steps))
maxTSP <- TSP[maxTSPRow,1]
```
The maximum number of steps is `r maxSteps`. This was found in interval `r maxTSP`.

#Number of NAs
```{r}
sum(is.na(total$steps))
```

#Inputing Missing Values
Using the medians at every 5 min, I replaced the values of NAs by the medians.


```{r}
activity2 <- activity
aggSteps <- aggregate(steps ~ interval, data = activity2, mean, na.rm=TRUE)

for (i in 1:length(activity2$steps)) {
if(is.na(activity2$steps[i])) {
index <- which(activity2$interval[i] == aggSteps$interval)
activity$steps[i] <- aggSteps$steps[index]
}
}
```

#Average of Steps Each Day
```{r}
total.imp <- aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
med.total2 <- median(total.imp$steps)
mean.total2 <- mean(total.imp$steps)
```

The mean number of steps taken with imputed values are `r mean.total2`. The median number of steps taken with imputed values are `r med.total2`.

That compares to the original dataset's mean and median of 
`r mean.total` and `r med.total` respectively.


#histogram of imputed dataset
```{r}
with(total.imp, hist(steps, breaks = seq(0,25000,1000)))
```

# Distinguishing weekend or weekday
```{r}
activity2['daytype'] <- weekdays(as.Date(activity2$date))
activity2$daytype[activity2$daytype == "Sunday"] <- "weekend"
activity2$daytype[activity2$daytype == "Saturday"] <- "weekend"
activity2$daytype[activity2$daytype != "weekend"] <- "weekday"
```

#Graph by weekend or weekday
```{r}
qplot(interval, steps, data = activity2, 
      type = 'l', 
      geom=c("line"),
      xlab = "Interval", 
      ylab = "Number of steps", 
      main = "Weekday vs Weekend") +
  facet_wrap(~ daytype, ncol=1)
```
library(knitr)
knit2html(input= "PA1_template.Rmd")
